\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-09 ms.tex
update figures and text

We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
\figurename~\ref{fig:cmds} shows the \gaia\ data for this region:
The left panel shows the \gaia\ color-magnitude diagram, extinction corrected following the procedure used in \citet{Danielski:2018}, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions of all stars in this sky region (grey background density), and only stars in the CMD selection polygon (black markers).

@@

While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
We note that this analysis and the subsequent discussion only considers subregion (a) of \clustername, which dominates the total mass and number of stars in the cluster.
\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.

>>>>

We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
\figurename~\ref{fig:cmds} shows the \gaia\ data for this region:
The left panel shows the \gaia\ color-magnitude diagram, extinction corrected following the procedure used in \citet{Danielski:2018} \changes{and the coefficients from \citet{Babusiaux:2018}}, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions of all stars in this sky region (grey background density), and only stars in the CMD selection polygon (black markers).

@@

While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
\changes{In addition, uncertainty in the \gaia\ passbands can cause significant differences in \gaia\ \bprp\ color for very blue sources \citep{MAW:2018}.}
To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
We note that this analysis and the subsequent discussion only considers subregion (a) of \clustername, which dominates the total mass and number of stars in the cluster.
\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.
